---
title: "Negroni Week PDX Venue Map"
output: pdf_document
---

__This map__ of the Portland area bars participating in [Negroni Week](negroniweek.com) is provided without warranty. 

###Note on methods:  
1.  Venues were downloaded directly from the Negoni Week website.  
2.  GPS coordinates were derived from online sources including Bing and Open Maps.  
3.  Charity Type is categorized by me.  

```{r, echo=FALSE}
Directory <- "/Users/winstonsaunders/Documents/Negroni_week/"
file<-"Negroni_week_PDX.csv"

venues<-read.csv(paste0(Directory, file))
venues$index<-1:nrow(venues)


    ## center map
    mid_lon=(min(venues$longitude)+max(venues$longitude))/2
    mid_lat=(min(venues$latitude)+max(venues$latitude))/2



```

#Number of venues by Charity Type.  

```{r echo=FALSE, message=FALSE, results="asis", warning=FALSE}
require(xtable)
venues_cats<-as.data.frame(t(table(venues$Type)))[,c(2,3)]
colnames(venues_cats)<-c("Charity Type", "Number")
print(xtable(venues_cats), floating=FALSE, comment=FALSE)
```

#Number of venues by Zip Code  

Only zip codes with three or more venues listed  

```{r echo=FALSE, message=FALSE, results="asis"}
require(xtable)
venues_cats<-as.data.frame(t(table(venues$Postal...Zip.Code)))[,c(2,3)]
colnames(venues_cats)<-c("Charity Type", "Number")

print(xtable(venues_cats[venues_cats$Number>2,]), floating=FALSE, comment=FALSE)
```

#Greater Portland Area Map  


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, results='asis'}
require(ggmap)
require(mapproj)

##Subset data by crime
## here focus on only top crimes
        ##get map data
        map <- get_map(source="google", maptype="roadmap", location = c(lon = mid_lon, lat = mid_lat), zoom = 12)
        ##generate map
        map1 <- ggmap(map) 

        ## 
        map1<-map1 + geom_point(aes(x = longitude, y = latitude, color=factor(Type)), data = venues, alpha = .8, size = 4) 
        map1<-map1+theme(legend.title=element_blank())
        map1<-map1+ggtitle("Negroni Week Venues and Charity Type")
        print(map1)
```

#Downtown Map

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6}
require(ggmap)
require(mapproj)

##Subset data by crime
## here focus on only top crimes
        ##get map data
        map <- get_map(source="google", maptype="roadmap", location = "Portland", zoom = 14)
        ##generate map
        map1 <- ggmap(map) 

        ## 
        map1<-map1 + geom_point(aes(x = longitude, y = latitude, color=factor(Type)), data = venues, alpha = .8, size = 4) 
        map1<-map1+theme(legend.title=element_blank())
        set.seed(8765309)
        map1<-map1+geom_text(data=venues, aes(x = longitude, y = latitude,label=index), size=2.5, position = position_jitter(w = 0.0005, h = 0.0005))
        map1<-map1+ggtitle("Negroni Week Venues and Charity Type")
        print(map1)
```
  

            
#Venue List   



```{r, echo=FALSE, results="asis", message=FALSE}

require(xtable)

venues_table=as.data.frame(venues[,c(1,3)])


venues_table1<-xtable(venues_table[1:40,])
venues_table2<-xtable(venues_table[40:58,])



print(venues_table1, floating=FALSE, comment=FALSE)
cat(".")
print(venues_table2, floating=FALSE, comment=FALSE)


 
```

```{r echo=FALSE}
cat("maps by ggmap():/n")
cat("D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2. The R Journal,
  5(1), 144-161. URL http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf /n")
```